Performance of Jellyfish Optimiser on Projection Pursuit Problems

### 2024-01-29 optim.qmd
more on the structure of the paper

---
title: Short Paper
subtitle: A Short Subtitle
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliations: 
        - id: some-tech
          name: Some Institute of Technology
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Bob Security
    email: bob@example.com
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
  - name: Cat Memes
    email: cat@example.com
    affiliations:
        - ref: another-u
    note: Yet another author footnote.
  - name: Derek Zoolander
    email: derek@example.com
    affilations:
        - ref: some-tech
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - projection pursuit
  - optimization
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Multivariate Analysis
      formatting: preprint
      model: 3p
      cite-style: super
---

# Introduction

The contributions of this paper are two folds. First, we provide proofs to demonstrate certain optimisers are for certain projection pursuit index functions. Second, we compare the performance of a collection of optimisers on a set of index function with different features and provide recommendations for analysts in practical problems.  @sec-background introduces the projection pursuit method, including the indexes function and optimisation. Section @sec-theory presents the proof on [...]. Section @sec-simulation presents the experimental results. Section @sec-conclusion concludes the paper.

# Projection pursuit, index functions and optimisation {#sec-background}

# [Theoretical results] {#sec-theory}

# [Simulation study] {#sec-simulation}

# Conclusion {#sec-conclusion}

>>>>

---
title: Performance of Jellyfish Optimiser on Projection Pursuit Problems
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliations: 
        - id: some-tech
          name: Some Institute of Technology
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    attributes:
        corresponding: true
  - name: Bob Security
    email: bob@example.com
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
  - name: Cat Memes
    email: cat@example.com
    affiliations:
        - ref: another-u
  - name: Derek Zoolander
    email: derek@example.com
    affilations:
        - ref: some-tech
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - projection pursuit
  - optimization
  - jellyfish optimiser
date: last-modified
bibliography: bibliography.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal of Multivariate Analysis
      formatting: preprint
      model: 3p
      cite-style: numbername
---

*Let's use British English ("American or British usage is accepted, but not a mixture of these")*

# Introduction [Nicolas and Jessica]

The rest of the paper is organised as follows: @sec-background introduces the projection pursuit method, including the indexes function and optimisation. @sec-theory introduces the jellyfish optimiser and proposes mathematical expressions to measure the . @sec-simulation applies the jellyfish optimiser through different projection pursuit problems with varying dimensions and index functions. @sec-conclusion concludes the paper.

# Projection pursuit, index functions and optimisation [Di and Sherry] {#sec-background}

# The jellyfish optimiser and property for good optimisers [Nicolas and Jessica] {#sec-theory}

The jellyfish optimiser [@chou_novel_2021] ...

@laa_using_2020 has proposed five criteria for assessing projection pursuit indexes (smoothness, squintability, flexibility, rotation invariance, and speed). Since not all the properties affects the optimisation, here we define the three relevant properties (smoothness, squintability, and speed) mathematically and show that the jellyfish optimiser ...

# Application [Di and Sherry] {#sec-simulation}

The jellyfish optimiser has been implemented in the tourr package [@wickham_tourr_2011] and we will use the diagnostic plots proposed in the ferrn package [@RJ-2021-105] to visualise the optimisation process.

## Going beyond 10D

The pipe-finding problem is initially used to investigate indexes and optimisers in @laa_using_2020, and we extend it from a 6D problem to a 12D problem.

Jellyfish optimiser, as a multi-start algorithm, is efficient in [...] for high-dimensional problems

## On skewness and kurtosis index

## Another data example

# Conclusion [Di and Sherry] {#sec-conclusion}

### 2024-01-29 optim.tex
more on the structure of the paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  super,
  preprint,
  3p]{elsarticle}

@@

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal of Multivariate analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Short Paper},
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={projection pursuit, optimization},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Short Paper \\\large{A Short Subtitle} }
\author[1]{Alice Anonymous%
\corref{cor1}%
\fnref{fn1}}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
\fnref{fn2}}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

@@

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}

\fntext[fn2]{Yet another author footnote.}

@@

\begin{keyword}
    projection pursuit \sep 
    optimization
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The contributions of this paper are two folds. First, we provide proofs
to demonstrate certain optimisers are for certain projection pursuit
index functions. Second, we compare the performance of a collection of
optimisers on a set of index function with different features and
provide recommendations for analysts in practical problems.
Section~\ref{sec-background} introduces the projection pursuit method,
including the indexes function and optimisation. Section
Section~\ref{sec-theory} presents the proof on {[}\ldots{]}. Section
Section~\ref{sec-simulation} presents the experimental results. Section
Section~\ref{sec-conclusion} concludes the paper.

\hypertarget{sec-background}{%
\section{Projection pursuit, index functions and
optimisation}\label{sec-background}}

\hypertarget{sec-theory}{%
\section{{[}Theoretical results{]}}\label{sec-theory}}

\hypertarget{sec-simulation}{%
\section{{[}Simulation study{]}}\label{sec-simulation}}

\hypertarget{sec-conclusion}{%
\section{Conclusion}\label{sec-conclusion}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number,
  preprint,
  3p]{elsarticle}

@@

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal of Multivariate Analysis}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num-names}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Performance of Jellyfish Optimiser on Projection Pursuit Problems},
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={projection pursuit, optimization, jellyfish optimiser},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Performance of Jellyfish Optimiser on Projection Pursuit
Problems}
\author[1]{Alice Anonymous%
\corref{cor1}%
}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

@@

\cortext[cor1]{Corresponding author}

@@

\begin{keyword}
    projection pursuit \sep optimization \sep 
    jellyfish optimiser
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable]}{\end{tcolorbox}}\fi

\emph{Let's use British English (``American or British usage is
accepted, but not a mixture of these'')}

\hypertarget{introduction-nicolas-and-jessica}{%
\section{Introduction {[}Nicolas and
Jessica{]}}\label{introduction-nicolas-and-jessica}}

The rest of the paper is organised as follows:
Section~\ref{sec-background} introduces the projection pursuit method,
including the indexes function and optimisation.
Section~\ref{sec-theory} introduces the jellyfish optimiser and proposes
mathematical expressions to measure the . Section~\ref{sec-simulation}
applies the jellyfish optimiser through different projection pursuit
problems with varying dimensions and index functions.
Section~\ref{sec-conclusion} concludes the paper.

\hypertarget{sec-background}{%
\section{Projection pursuit, index functions and optimisation {[}Di and
Sherry{]}}\label{sec-background}}

\hypertarget{sec-theory}{%
\section{The jellyfish optimiser and property for good optimisers
{[}Nicolas and Jessica{]}}\label{sec-theory}}

The jellyfish optimiser \citep{chou_novel_2021} \ldots{}

\citet{laa_using_2020} has proposed five criteria for assessing
projection pursuit indexes (smoothness, squintability, flexibility,
rotation invariance, and speed). Since not all the properties affects
the optimisation, here we define the three relevant properties
(smoothness, squintability, and speed) mathematically and show that the
jellyfish optimiser \ldots{}

\hypertarget{sec-simulation}{%
\section{Application {[}Di and Sherry{]}}\label{sec-simulation}}

The jellyfish optimiser has been implemented in the tourr package
\citep{wickham_tourr_2011} and we will use the diagnostic plots proposed
in the ferrn package \citep{RJ-2021-105} to visualise the optimisation
process.

\hypertarget{going-beyond-10d}{%
\subsection{Going beyond 10D}\label{going-beyond-10d}}

The pipe-finding problem is initially used to investigate indexes and
optimisers in \citet{laa_using_2020}, and we extend it from a 6D problem
to a 12D problem.

Jellyfish optimiser, as a multi-start algorithm, is efficient in
{[}\ldots{]} for high-dimensional problems

\hypertarget{on-skewness-and-kurtosis-index}{%
\subsection{On skewness and kurtosis
index}\label{on-skewness-and-kurtosis-index}}

\hypertarget{another-data-example}{%
\subsection{Another data example}\label{another-data-example}}

\hypertarget{sec-conclusion}{%
\section{Conclusion {[}Di and Sherry{]}}\label{sec-conclusion}}
